Probability Aggregation: Dynamic Hierarchical Modeling of Expert Beliefs in Geopolitical Events

### 2013-08-21 paper.tex
Edited Abstract

\begin{abstract}
Most research on subjective probability aggregation concentrates on procedures that consult the expert advice only once before making the final aggregation. This paper makes an advance towards unexplored areas of probability aggregation by considering a dynamic context with a time period during which the experts are allowed to update their beliefs. The analysis is performed on a real-world dataset that includes over 2,300 experts making probability forecasts on a number of 166 different international political events. The model is able to take  into account the forecaster's level of self-reported expertise and produce aggregate probabilities that are sharp and well-calibrated both in- and out-of-sample. Using the aggregate probabilities as the no-bias reference-line, the groups of experts with different levels of self-reported expertise are found to be under-confident, with the level of under-confidence decreasing as a function of self-reported expertise.
\end{abstract}

>>>>

\begin{abstract}
Most subjective probability aggregation procedures use a single
probability judgement from each expert, even though it is common for
experts studying real problems to update their probability estimates
over time.  This paper makes an advance towards unexplored areas of
probability aggregation by considering a dynamic context in which
experts are allowed to update their beliefs at random intervals.  We
demonstrate our method on a real-world dataset that includes over
2,300 experts making multiple probability forecasts on different
subsets of 166 different international political events. We present a
dynamic model that takes into account the forecaster’s level of
self-reported expertise and produces aggregate probabilities that are
sharp and well-calibrated both in- and out-of-sample. Using the
aggregate probabilities as the no-bias reference-line, the lower the
self-reported expertise in a group, the more under-confident it is
found to be.
\end{abstract}
